---
title: "cloud"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cloud}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(revdepcheck)
```

# Running reverse dependencies in the cloud

revdepcheck now supports running reverse dependencies in the AWS cloud, via a suite a functions all prefixed with `cloud_*()`.
This service is currently only available to be used by RStudio employees, but we hope to offer this service for the broader R community in the future.

## Setup

Set the `RSTUDIO_CLOUD_REVDEP_KEY` environment variable to the value of your AWS authentication key, provided to you by RStudio DevOps.
Add this key to your `.Renviron` file with `usethis::edit_r_environ()` and restart R.

Then install and configure the `aws` command line tool.

```shell
brew install awscli
aws configure sso
```

This will start an interactive process for generating a configuration file in `~/.aws/config`.

- You will be asked for an SSO start URL. Enter https://rstudio.awsapps.com/start.
- You will be asked for an SSO Region. Enter us-east-2.
- Your browser will open to an Okta single sign on page. Sign in then return to the terminal.
- Select RStudio Main as the AWS account (Note that RStudio Tidyverse is not the correct account for this).
- Select us-east-1 as the default region (this may already be the default).
- Select json as the default output format (this may already be the default).
- Specify a profile name, or leave it as TidyverseTeam.

Open the newly generated config text file in `~/.aws/config`. Make the newly generated profile your default by naming it `[default]` if it isn't already. Save and close the file.

For more information, look here:

- [Tettra post on AWS SSO](https://app.tettra.co/teams/rstudio/pages/aws-single-sign-on#header-ek8lr-interactive-setup)
- [Okta post on AWS SSO](https://www.okta.com/blog/2020/05/how-okta-aws-sso-simplifies-admin-and-adds-cli-support/)

## Usage

**Note** If you are going to be running 500+ tests and are using a development dependency (e.g. `Remote: org/pkg`) you may exhaust the GitHub API limits. A workaround is to use a 'url' remote, e.g. `Remote: url::https://github.com/org/pkg/archive/master.tar.gz`, which does not use the GitHub API.

```r
# Kickoff a new check
# The devel package is automatically built from the current
# working directory, or specify a pre-built package with `tarball`.
cloud_check()

# Follow current status of the job
cloud_status()

# Cancel a job
cloud_cancel()

# Retrieve results (if needed) and show a summary
cloud_summary()

# Retrieve results (if needed) and generate a markdown report
cloud_report()

# Retrieve details of a specfic package
cloud_details(, "pkgXYZ")

# Plot running time for each package in a job
cloud_plot()

# Email maintainers with failures
cloud_email()

# Retrieve packages that broke in a given job
cloud_broken()

# Open a web browser to the AWS job pane for the current job
cloud_browse()

# Open the browser to the AWS job for a particular package
# Useful for debugging why a particular job failed
cloud_browse(package = "xyz")
```

The functions all keep track of the most recently submitted `job_id`, so assuming you only have one job in a given R session you can call the functions without additional parameters.
Provide the `job_id` explicitly otherwise, results write to `revdep/{job_id}`.

The `cloud_*()` functions assume your current working directory is in the root directory of the package you are trying to run reverse dependencies for.
If this is not the case all `cloud_*()` functions take a `pkg` parameter, so you can specify a different directory if needed.
